A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2012-05-20 docs/paper.tex
fixed patrascu citation

\begin{abstract}
Here we implement simple tabulation hashing with linear probing in Python
dictionary based on the recent theoretical result of Patrascu et al. Although
we achieved significant performance wins on synthetic benchmarks, on real
benchmarks our wins were only on the order of 4\%.  When viewed as a whole, the
extra memory bandwidth
and latency required to compute the simple tabulation hash are too large to
justify the dictionary speedup garnered by switching to simple tabulation hashing and linear probing.
\end{abstract}

@@

Patrascu et al. [2] describe simple tabulation hashing for fixed key widths.  For implementing this new hashing scheme, first we needed to figure out a variant of simple tabulation hashing for variable length strings that does not require a table for every possible index (we could potentially cycle through a fixed set of tables).  Performing table lookups is potentially an expensive operation with lots of cache hits mitigating the better cache behavior of linear probing so we will have to be careful about how to implement this. In the following section we explain the implementation details of our approach to these problems.

>>>>

\begin{abstract}
Here we implement simple tabulation hashing with linear probing in Python
dictionary based on the recent theoretical result of P\v{a}tra\c{s}cu et al. Although
we achieved significant performance wins on synthetic benchmarks, on real
benchmarks our wins were only on the order of 4\%.  When viewed as a whole, the
extra memory bandwidth
and latency required to compute the simple tabulation hash are too large to
justify the dictionary speedup garnered by switching to simple tabulation hashing and linear probing.
\end{abstract}

@@

P\v{a}tra\c{s}cu et al. \cite{mihai} describe simple tabulation hashing for fixed key widths.  For implementing this new hashing scheme, first we needed to figure out a variant of simple tabulation hashing for variable length strings that does not require a table for every possible index (we could potentially cycle through a fixed set of tables).  Performing table lookups is potentially an expensive operation with lots of cache hits mitigating the better cache behavior of linear probing so we will have to be careful about how to implement this. In the following section we explain the implementation details of our approach to these problems.
